\documentclass[10pt]{article}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx,ctable,booktabs}
\usepackage{fancyhdr}
\usepackage{lscape}
\usepackage{multirow}
\pagestyle{fancy}
\setcounter{page}{0}
\lhead{MIT Security Training CTF 2014} \rhead{\thepage}
\lfoot{TEAMNAME}
\renewcommand{\footrulewidth}{.3pt}
\setlength\voffset{-0.25in}
\setlength\textheight{648pt}


\begin{document}
\begin{landscape}
\thispagestyle{empty}
\vspace*{\fill}
\begingroup
\centering
\begin{center}
{\bf\Huge TEAMNAME}
\end{center}
\endgroup
\vspace*{\fill}
\end{landscape}
\newpage
\begin{center}
\section*{Briefing}
\end{center}
You've been recruited to help recover the Tesseract, a cache of scientific data
left behind by John Smith, the founder of a small scientific thinktank doing
research into all kinds of strange areas of science. Since his demise, the
world's governments and various private institutions have been working to gain
access to the vault containing the Tesseract, however until now no-one has had
any luck discovering the password that allows access to the vault. Rumors have
recently begun circulating from those who were close to John Smith, that the
answer lies in the various scientific outposts and probes that John Smith sent
out to the wider solar system and into the Earth's crust over the course of his
life.

These documents contains all the information we have on each of the 25 sites
that we believe contain information that is vital to unlock the secret of the
Tesseract. The information you are looking for will be of the form
{\tt tesseract2014\{FLAG\}}. As you discover this information, you'll be able to
turn it in to the data terminal we've recovered to verify the validity of the
information. Different sites are worth different amounts. (Only the FLAG, and
not the surrounding {\tt tesseract2014\{\}}) Unfortunately, you are not alone in
this quest and there are other groups that are chasing down these leads and
trying to gain control of the vault. Hopefully you'll be able to discover the
secrets that are contained in these sites, and open the vault containing the
Tesseract before others do.

Only the top 8 teams will have the opportunity to provide the 9 symbol code that
could potentially open the Tesseract Vault. Placement is determined by the
number of points you've gained, and then determined by earliest final submission
in case of ties. The top team will receive a \$500 finder's fee, while the
second place team will receive a \$250 better luck next time award. Whoever
delivers the secret of the Tesseract will also receive a \$250 recognition
award.

Additionally, there are a number of academics and hobbyists who are also looking
into these sites, and trying to discover their secrets. They are livestreaming
their discoveries and methodologies, and we will try broadcasting whenever they
release a new presentation on one of the sites. One of our representatives will
occasionally come around to see which sites we should steer the academics and
hobbyists towards researching and releasing details on.

The information you need to verify pieces of information and to access our
secure uplink is:
\vspace{0.2in}
{\tt\large
\begin{center}
\begin{tabular}{| r | l |}
\hline
Team Name & TEAMNAME\\\hline
Team Email & TEAMEMAIL\\\hline
Username & USERNAME\\\hline
Password & PASSWORD\\\hline
Neptune Uplink Username & NEPTUNEUSER\\\hline
Neptune Uplink Password & NEPTUNEPASS\\\hline
Starting Point & http://REMOTE\\\hline
IRC Channel & \#mitctf on irc.freenode.net\\\hline
\end{tabular}
\end{center}
}

{\tt TL;DR:}
\begin{itemize}
\item There are a total of 25 sites/services with flags of the form {\tt
    tesseract2014\{FLAG\}}.
\item You may submit flags at the terminal using your login. Don't include {\tt
    tesseract2014\{\}}.
\item Each service has a point value. Placement is determined by score, and then
  by time.
\item The top 8 teams will have a chance to submit the ``Final Code''.
\item \$500 for 1st, \$250 for 2nd, \$250 for solving the ``Final Code''.
\item Every 90 minutes or so, the organizers will go through solving a
  challenge and announce the next challenge to be deconstructed. The flag can
  then be submitted for points.
\item The organizers will ask all the teams about which particular challenges
  they'd like to see solved.
\end{itemize}
\newpage
\input{services/rev400.tex}\newpage
\input{services/explt100.tex}\newpage
\input{services/steg100.tex}\newpage
\input{services/explt400.tex}\newpage
\input{services/phys100.tex}\newpage
\input{services/explt300.tex}\newpage
\input{services/recon100.tex}\newpage
\input{services/rev300.tex}\newpage
\input{services/for200.tex}\newpage
\input{services/phys200.tex}\newpage
\input{services/for100.tex}\newpage
\input{services/phys500.tex}\newpage
\input{services/explt500.tex}\newpage
\input{services/crypt100.tex}\newpage
\input{services/phys300.tex}\newpage
\input{services/web200.tex}\newpage
\input{services/crypt300.tex}\newpage
\input{services/explt200.tex}\newpage
\input{services/crypt200.tex}\newpage
\input{services/misc100.tex}\newpage
\input{services/for300.tex}\newpage
\input{services/rev200.tex}\newpage
\input{services/web100.tex}\newpage
\input{services/rev100.tex}\newpage
\input{services/phys400.tex}\newpage
\input{services/bonus100.tex}\newpage
\input{services/bonus200.tex}\newpage
\input{services/bonus300.tex}\newpage

\begin{center}
\section*{Site Flags}
\begin{tabular}{| c | c |}
\hline
\multirow{2}{*}{\bf\Large Site} & \hspace*{1.6in}\multirow{2}{*}{\bf\Large Flag}\hspace*{1.6in}\\&\\\hline
\multirow{2}{*}{{\tt Ancient Functions}} &\\&\\\hline
\multirow{2}{*}{{\tt Asteroid Mining}} &\\&\\\hline
\multirow{2}{*}{{\tt Awesome Images}} &\\&\\\hline
\multirow{2}{*}{{\tt Beaten to Mars}} &\\&\\\hline
\multirow{2}{*}{{\tt Combo Breaker}} &\\&\\\hline
\multirow{2}{*}{{\tt Distant Communications}} &\\&\\\hline
\multirow{2}{*}{{\tt Eldritch Scientist}} &\\&\\\hline
\multirow{2}{*}{{\tt Esoteric Dumps}} &\\&\\\hline
\multirow{2}{*}{{\tt Exposed to Attackers}} &\\&\\\hline
\multirow{2}{*}{{\tt Jupiter Tamper}} &\\&\\\hline
\multirow{2}{*}{{\tt Listening In}} &\\&\\\hline
\multirow{2}{*}{{\tt Lost in Centauri}} &\\&\\\hline
\multirow{2}{*}{{\tt Neptune Over The Sea}} &\\&\\\hline
\multirow{2}{*}{{\tt One Pad To Rule Them All}} &\\&\\\hline
\multirow{2}{*}{{\tt Pinned to the Table}} &\\&\\\hline
\multirow{2}{*}{{\tt Pluto Squares}} &\\&\\\hline
\multirow{2}{*}{{\tt Pretty Global Privacy}} &\\&\\\hline
\multirow{2}{*}{{\tt Remotely Executable Probes}} &\\&\\\hline
\multirow{2}{*}{{\tt Rolling Keys}} &\\&\\\hline
\multirow{2}{*}{{\tt Secretly Constrained}} &\\&\\\hline
\multirow{2}{*}{{\tt Sedna Caught}} &\\&\\\hline
\multirow{2}{*}{{\tt Space Cinema}} &\\&\\\hline
\multirow{2}{*}{{\tt Space Contacts}} &\\&\\\hline
\multirow{2}{*}{{\tt Star Noise}} &\\&\\\hline
\multirow{2}{*}{{\tt Stuck in Space}} &\\&\\\hline
\end{tabular}
\end{center}
\end{document}
